### 2020-03-31 papers.tex
Remove dead spaces etc
Fix most of the names to the point it compiles

% TODO
%  [ ] move each commentary directly after each long paper
%  [ ] fill in titles of commentaries
%  [ ] fill in full author for each commentary

@@

\insertmydocument{chapter}{Relationships between narrative and argumentation. In defence of a functional account}{Guillermo Sierra Catalán}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19

@@

\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{Hédi Virág Csordás}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25

@@

\insertmydocument{chapter}{An indexical characterization of disagreement based on possible worlds semantics}{Léa Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35

@@

\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Kišiček}{pdfs/regular/60regularKisicek.docx.pdf} % 60

@@

\insertmydocument{chapter}{Argument, justification and inquiry: a pragmatist approach}{Federico Ezequiel López}{pdfs/regular/75regularLopez.doc.pdf} % 75

@@

\insertmydocument{chapter}{Separate opinions as an argumentative activity type}{H. José Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98

@@

\insertmydocument{chapter}{Inference to the Best Metaphor}{Cristián Santibáñez}{pdfs/regular/107regularSantibanez.docx.pdf} % 107

@@

\insertmydocument{chapter}{Explaining away and the propensity interpretation of probability: the case of unequal priors}{Alice Liefgreen,  Marko Tešić}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116

@@

\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval reception}{Gustavo Fernández Walker,  Ana María Mora-Márquez}{pdfs/regular/122regularWalker.docx.pdf} % 122

>>>>

% TODO
% [ ] move each commentary directly after each long paper
% [ ] fill in titles of commentaries
% [ ] fill in full author for each commentary
% [ ] Latexify all the weird unicode names (https://en.wikibooks.org/wiki/LaTeX/Special_Characters)

@@

\insertmydocument{chapter}{Relationships between narrative and argumentation. In defence of a functional account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19

@@

\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{H\'{e}di Vir\'{a}g Csord\'{a}s}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25

@@

\insertmydocument{chapter}{An indexical characterization of disagreement based on possible worlds semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35

@@

\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60

@@

\insertmydocument{chapter}{Argument, justification and inquiry: a pragmatist approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75

@@

\insertmydocument{chapter}{Separate opinions as an argumentative activity type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98

@@

\insertmydocument{chapter}{Inference to the Best Metaphor}{Cristi\'{a}n Santib\'{a}\~{n}ez}{pdfs/regular/107regularSantibanez.docx.pdf} % 107

@@

\insertmydocument{chapter}{Explaining away and the propensity interpretation of probability: the case of unequal priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116

@@

\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
